\section{Infosheet}

\textbf{Project Title}

Decentral market
\\
\\
\textbf{Client organisation}

TU Delft
\\
\\
\textbf{Date of final presentation}

09-07-2015
\\
\\
\textbf{Description}

The goal was to create a proof of concept for a decentralised market where users can trade commodities for real money, with no central point of failure or governing authority.
Few similar applications exists, those that do focus on BitCoin as a currency.
Development occurred in sprints of one week, with the team working daily side by side to tackle the project.
The end result is Tsukiji, an application where users can trade goods in a decentralised manner using real money.
As a proof of concept, there are still many issues regarding trust, privacy, and user experience to be solved in future releases.
\\
\\
\textbf{Members of the Project Team}
\\

\textbf{Michael The} is working on his Bachelor Computer Science at the TU Delft.
In his spare time he plays too many video games.
He is also active as a freelance python programmer for various companies.
Michael is mostly responsible for designing the protocol and testing the application.
\\

\textbf{Hugo Reinbergen} spends most of his spare time organising events for the Delftsche Studenten Bond, gaming, creating video effects and researching anonymity and system security.
Hugo is responsible for the cryptography, the gossip implementation and the PayPal interaction.
\\

Both team members contributed to writing the report and preparing the final presentation.
\\
\\
\textbf{Client}

Johan Pouwelse, TU Delft
\\
\textbf{Coach}

Raynor Vliegendhart, TU Delft
\\
\textbf{Contact Person}

Johan Pouwelse (\href{mailto:J.A.Pouwelse@tudelft.nl}{J.A.Pouwelse@tudelft.nl})

Michael The	(\href{mailto:mcgthe@gmail.com}{mcgthe@gmail.com})
\\
\\
The final report for this project can be found at: \url{http://repository.tudelft.nl}